Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-15 paper/section_2_literature.tex
Add model figure

\begin{figure*}[t]
    \begin{center}
    \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
    \end{center}
       \caption{Overall architecture of the model.}
    \label{fig:short}
 \end{figure*}

>>>>

\begin{figure*}[t]
   \begin{center}
		\includegraphics[width=0.99\linewidth, frame]{figures/figure_2.pdf}
	\end{center}
       \caption{Overall architecture of the model. On the left is the decoder,
       which takes as input a byte-pair token (e.g. 14980 represents the middle
       token ``arsh'' in ``Varshini''). The grey arrows inside the decoder
       indicate the convolutions in each layer (we only show the convolutions
       in the final time step). In each convolution layer, we attend to the
       three domains: article (green lines), image patches (yellow lines) and
       faces (orange lines). The grey triangles are switches to determine if we
       should copy or not. If we copy, we attend to the article embeddings to
       copy the most attended token (dashed black line). The decoder outputs
       are byte-pair tokens, which are then combined to form whole words.}
    \label{fig:model}
 \end{figure*}
